---
title: "hw5"
author: "Jiabei Wang"
date: "11/1/2018"
output: github_document
---
## Problem 1
```{r}
library(tidyverse)
library(readxl)
library(rvest)
library(purrr)
set.seed(1)
file_names =list.files(path = "./data") 
path = str_c("./data/", file_names)
total_table = tibble(x = file_names) %>% 
  mutate(output = map(path, read_csv) ) %>%
unnest() %>%
janitor::clean_names()%>% 
separate(x, into = c("arm", "subject"), sep = "_") %>%
  separate(subject, into = c("subject", "delete")) %>%
select(-delete)%>%
gather(key = week_of_study, value = Value, week_1:week_8) %>%
separate(week_of_study, into = c("a", "week"), sep = "_")%>%
  select(-a) %>%
janitor::clean_names()%>%
  mutate(subject = as.factor(subject), arm = as.factor(arm)) %>%
group_by(subject, arm)
##make a spaghetti plot
ggplot(total_table, aes(x = week, y = value, group = (arm:subject), color = arm)) + 
    geom_line() + 
    theme(legend.position = "bottom") + labs(title = "Longitudial Plot",
    x = "Week",
    y = "Observations on Value"
  ) 

```
From the spaghetti plot, the control and experiment arm have approximately same observations on value, but after following up, the value of experimental group has an obvious increasing trend while the control group maintain almost unchanged. 

## Problem 2
```{r}
homicides_data = read_csv(file = "./data2/homicide-data.csv")%>% 
mutate(city_state = paste(city, state)) %>%
select(-city) %>% 
  select(-state)
```
The raw data contains `r nrow(homicides_data)` observations, and it contains `r ncol(homicides_data)` variables. Homicides in 50 US cities are recorded in this dataset, 

```{r}
homicides_data %>%
group_by(city_state, disposition) %>%
group_by(disposition) %>%
  summarize(n = n())
```

```{r}
library(broom)
city_homicides = read_csv(file = "./data2/homicide-data.csv")%>% 
mutate(city_state = paste(city, state)) %>%
select(-city, -state) %>%
group_by(city_state, disposition)%>%
  summarize(n = n()) %>%
spread(key = disposition, value = n) %>%
  janitor::clean_names() %>%
  replace(is.na(.),0)%>%
mutate(unsolved_homicides = closed_without_arrest + open_no_arrest) %>%
mutate(total = unsolved_homicides + closed_by_arrest) %>%
select(-closed_by_arrest, -closed_without_arrest,-open_no_arrest ) 

```


```{r}
baltimore = city_homicides %>%
  filter(city_state =="Baltimore MD")
prop.test_baltimore = prop.test(baltimore$unsolved_homicides, baltimore$total, correct = FALSE)

broom::tidy(prop.test_baltimore) [,c(1,5,6)]
# select(estimate, conf.low, conf.high)
```

```{r}
prop.testp = function(a){
 b = prop.test(a$unsolved_homicides, a$total) 
  broom::tidy(b) [,c(1,5,6)]
  } 

prop.testp(city_homicides[1,])
output = 
  city_homicides %>%
  nest(city_state, unsolved_homicides:total) %>% 
  mutate(prop = map(data,  prop.testp )) %>% 
  unnest() %>%

  mutate(city_state = fct_reorder(factor(city_state),estimate)) 
  
  ggplot(output, aes(x = city_state, y = estimate, color = city_state)) + 
  geom_point() + 
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +  
    theme(text = element_text(size = 6), 
          axis.text.x = element_text(angle = 60),
          legend.key.size= unit(0.05,"cm")) +

    labs(title = "Estimate and CI Across Cities",
    x = "city_state",
    y = "estimate"
  ) 


  
  

```

